---
title: "RS3 Day 14"
author: "Saina Shibili"
date: "2023-04-12"
output:
  word_document: default
  html_document: default
---

20a. (0.907,1.233)
``` {r question 20a}
library(readr)
HighPeaks <- read_csv("Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/HighPeaks.csv")

ltlm = lm(Length~Time, data=HighPeaks)
summary(ltlm)

t=qt(.95, df=44)
1.07+t*0.097
1.07-t*0.097
```
20b. The distribution is relatively bell shaped with slight skew to the right
``` {r question 20b}
library(mosaic)
set.seed(1234)
N=5000
manyslopes = do(N)*lm(Length~Time, data=resample(HighPeaks))
histogram(manyslopes$Time, xlab="slopes")
```
20c. Both values are fairly close to the original regression values.
``` {r questopm 20c}
mean(manyslopes$Time)
sd(manyslopes$Time)
```
20d. (0.878, 1.276)
20e. (0.913, 1.311)
20f. (0.843, 1.241)
20g. Yes, they are all similar but slightly vary between each other

21. 
``` {r question 21}
qlower = quantile(manyslopes$sigma, 0.025)
qupper = quantile(manyslopes$sigma, 0.975)
c(qlower, qupper)

z=qnorm(0.95)
SE = sd(manyslopes$sigma)
m = mean(manyslopes$sigma)
selower = m - z*SE
seupper = m + z*SE
c(selower, seupper)

diffup = m - qlower
diffdown = qupper - m
newlower = m - diffdown
newupper = m + diffup
c(newlower, newupper)
```

23a. It looks like this distribution is fairly normal
``` {r question 23a}
SATGPA <- read_csv("Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/SATGPA.csv")

set.seed(333)
N=50
slopes = do(N)*lm(VerbalSAT~GPA, data=resample(SATGPA))
histogram(slopes$GPA)
qqnorm(slopes$GPA)
```
23b. Both intervals contain zero, showing its possible that there is no relationship between Verbal SAT and GPA.
``` {r question 23b}
qlower = quantile(slopes$GPA, 0.025)
qupper = quantile(slopes$GPA, 0.975)
c(qlower, qupper)

z=qnorm(0.95)
SE = sd(slopes$GPA)
m = mean(slopes$GPA)
selower = m - z*SE
seupper = m + z*SE
c(selower, seupper)
```

