---
title: "day 17 rs3"
author: "Saina Shibili"
date: "2023-04-18"
output:
  word_document: default
  html_document: default
---
6. b

7. d

11a. Random assignment is impossible because ethnicity cannot be assigned
11b. Random sampling is required for generalization; Yes

12a. Since this is a study, causation cannot be inferred. Similarly since the response variable is reported and not official, we cannot be sure of the data
12b. For this high school, students who report preferring heavy metal are more likely to report driving above 80 mph

14a. Since their are 4 groups, ANOVA is the test used
14b. The response variable is age, which is quantitative
14c. ANOVA doesn't require sample sizes to be equal
14d. Since random sampling is used, generalization can be done.

22a. No because then all of the data values would be higher than the mean
22b. Yes, the one negative residual would have to be very very large
22c. Yes, because the higher value could be closer to the mean
22d. Yes, because the two means could be different

27a. The minus group has less contacts than Mixed and Plus groups.
``` {r question 27a}
library(readr)
library(mosaic)
MouseBrain <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/MouseBrain.csv")

boxplot(Contacts~Genotype, data=MouseBrain)
favstats(Contacts~Genotype, data=MouseBrain)
```
27b. The normality and fitted v residuals plot shows that normality is met and that standard deviations are pretty close. The mice should also be independent of each other
``` {r question 27b}
genolm = lm(Contacts~Genotype, data=MouseBrain)
qqnorm(genolm$residuals)
plot(genolm$residuals~genolm$fitted.values) + 
  abline(0,0)
plot(genolm$residuals) +
  abline(0,0)
```

31a.
``` {r question 31a}
Amyloid <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/Amyloid.csv")

favstats(Abeta~Group, data=Amyloid)
```
31b. Since skew is shown, normality is not met, so the conditions for ANOVA are not necessarily met.
``` {r question 31b}
boxplot(Abeta~Group, data=Amyloid)
```

33a. DF|Occupation = 972-968 = 4; SS|Occupation = 206147-195149 = 10998; F = 2749/202 = 13.60891
33b. 5 since DF + 1 = 5
33c. Since the p-value is small, we see a significant difference between at least two of the occupations studied

38a. Ho --> The means of the groups are equal, Ha --> The means of the groups differ
38b. The residuals are about normal and show similar variability.
``` {r question 38b}
Meniscus <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/Meniscus.csv")

menilm = lm(Stiffness~Method, data=Meniscus)
qqnorm(menilm$residuals)
plot(menilm$residuals~menilm$fitted.values) + 
  abline(0,0)
plot(menilm$residuals) +
  abline(0,0)
```
38c. Since the p-value is relatively high, there is not evidence to suggest a difference between methods in this dataset.
``` {r question 38c}
menianova = aov(Stiffness~Method, data=Meniscus)
summary(menianova)
```

40a. Ho --> The means of the groups are equal, Ha --> The means of the groups differ
40b. The residuals are about normal and show similar variability.
``` {r question 40b}
menilm = lm(Displacement~Method, data=Meniscus)
qqnorm(menilm$residuals)
plot(menilm$residuals~menilm$fitted.values) + 
  abline(0,0)
plot(menilm$residuals) +
  abline(0,0)
```
40c.Since the p-value is relatively high, there is not evidence to suggest a difference between methods in this dataset.
``` {r question 40c}
menianova = aov(Displacement~Method, data=Meniscus)
summary(menianova)
```