---
title: "RS3 Day 13"
author: "Saina Shibili"
date: "2023-03-28"
output:
  word_document: default
  html_document: default
---

13. The mean birth weight for the reference group (Whites) is 117.87. Black babies are expected to weigh 117.87-7.31=110.56 ounces. Hispanic babies are expected to weigh 117.87+0.65=118.52. Babies of other races are expected to weigh 117.87-0.73=117.14

14a. The p-values from the t-tests indicate that black babies weight a statistically significant amount different than white babies while there is no statistical significance for the weights of hispanic and "other" babies.
14b. 1.7% of variability in this dataset is accounted for in this model.
14c. The F-value indicates that there is a statistically significant difference between at least two of the groups in the samples tested.

16a. The R-squared value is 75.55%
``` {r question 16a}
library(readr)
Caterpillars <- read_csv("Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/Caterpillars.csv")

lognassimlm = lm(LogNassim~LogMass, data=Caterpillars)
summary(lognassimlm)
```
16b. The R-squared value is 83.48% which is higher than part a.
``` {r question 16b}
Caterpillars$Instar1 = Caterpillars$Instar == 1
Caterpillars$Instar2 = Caterpillars$Instar == 2
Caterpillars$Instar3 = Caterpillars$Instar == 3
Caterpillars$Instar4 = Caterpillars$Instar == 4

instarlm = lm(LogNassim~Instar1+Instar2+Instar3+Instar4, data=Caterpillars)
summary(instarlm)
```
16c. -1.47367 indicates the mean of LogNassim for values with Instar = 5. Therefore, the mean of LogNassim for values with Instar = 1 is -1.47367 - 1.249 = -2.723
16d. The R-squared value is 83.61 which is greater than LogMass on its own but lower than the Instar model.
``` {r question 16d} 
bothlm = lm(LogNassim~LogMass+Instar1+Instar2+Instar3+Instar4, data=Caterpillars)
summary(bothlm)
```
16e. Since the p-value of LogMass is high, it is not needed in this model.
16f. Since the p-values of the Instar terms are all low, we are confident that this model is needed.

19a. 
``` {r question 19a}
BaseballTimes2017 <- read_csv("Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/BaseballTimes2017.csv")

baseballlm = lm(Time~Pitchers+Attendance, data=BaseballTimes2017)
summary(baseballlm)
```
19b. The R-squared value is 53.07%
19c. The new R-squared value is 5.192%
``` {r question 19c}
library(mosaic)
set.seed(1234)
BaseballTimes2017$RandomTime = shuffle(BaseballTimes2017$Time)
randomlm = lm(RandomTime~Pitchers+Attendance, data=BaseballTimes2017)
summary(randomlm)
```
19d. 
``` {r question 19d}
set.seed(4321)
N=10000
manycors = do(N)*cor(shuffle(Time)~Pitchers+Attendance, data=BaseballTimes2017)
manyr = manycors$cor^2
hist(manyr, xlab="correlation", main="")
```
19e. We would count the number of values that exceed our p-value (0.7458). Since we got a number close to 0, we believe the original R-squared value was unusually large.
``` {r question 19e}
sum(manyr>0.7458)/10000
```
19f. Since the F values were similar, we believe that both models are similarly effective