---
title: "RS3 Day 18"
author: "Saina Shibili"
date: "2023-04-26"
output:
  word_document: default
  html_document: default
---

53a.There appears to be a difference between the two groups
``` {r 53a}
library(readr)
OilDeapsorbtion <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/OilDeapsorbtion.csv")

stripchart(OilDeapsorbtion$diff~OilDeapsorbtion$Oil, method = "stack",
           offset = 0.5,
           pch = 19,
           col = "blue",
           xlab = "oil",
           ylab = "diff")
summary(OilDeapsorbtion$Oil)
```
53b. Since the p-value is fairly low, we assume there is a significant diffference between the two groups
```{r 53b}
t.test(OilDeapsorbtion$diff~OilDeapsorbtion$Oil)
```
53c. The p-value is around the same, at 0.006
```{r 53c}
aov(OilDeapsorbtion$diff~OilDeapsorbtion$Oil)
```
53d. Both p-values are around the same value.

55a. Yes
``` {r 55a}
stripchart(OilDeapsorbtion$diff~OilDeapsorbtion$Ultra, method = "stack",
           offset = 0.5,
           pch = 19,
           col = "blue",
           xlab = "ultra",
           ylab = "diff")
summary(OilDeapsorbtion$Ultra)
```
55b. The p-value is relatively high
``` {r 55b}
t.test(OilDeapsorbtion$diff~OilDeapsorbtion$Ultra)
```
55c. The p-value is similar at 0.77
``` {r 55c}
aov(OilDeapsorbtion$diff~OilDeapsorbtion$Oil)
```
55d. They are the same

57a. H0: The means equal 0, Ha: The means don't equal 0
57b. The residuals don't appear to be normal
``` {r 57a}
Meniscus <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/Meniscus.csv")

mlm = lm(FailureLoad~Method, data=Meniscus)
plot(mlm$residuals) + abline(0,0)
qqnorm(mlm$residuals)
hist(mlm$residuals)
```