---
title: "RS3 Day 20"
author: "Saina Shibili"
date: "2023-05-11"
output:
  word_document: default
  html_document: default
---

8. c

10a. Very different standard deviations
10b. It can be transformed for a better fit. Take 1-slope for the power to which the data should be transformed to.

43a. Yes the points suggest a line.
``` {r 43a}
library(readr)
library(dplyr)
Hawks <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/Hawks.csv")

stats_Hawks <- Hawks %>% 
  group_by(Species) %>% 
  summarise(mean_weight=mean(Weight, na.rm=T), sd_weight=sd(Weight, na.rm=T)) %>%
  as.data.frame()

stats_Hawks$logave = log(stats_Hawks$mean_weight)
stats_Hawks$logs = log(stats_Hawks$sd_weight)
plot(logs~logave, data=stats_Hawks) + abline(1.8, 0.5)
```
43b. it appears to be about 0.5
44b. A square root transformation

49a.
``` {r 49a}
Hawks$sqrtweight <- Hawks$Weight ** 0.5
Hawks %>% 
  group_by(Species) %>% 
  summarise(mean_weight=mean(sqrtweight, na.rm=T), sd_weight=sd(sqrtweight, na.rm=T))
```
49b. Mean is highest for RT and lowest for SS
``` {r 49b}
boxplot(Hawks$sqrtweight ~ Hawks$Species)
```
49c. Although all boxplots have similar variances now, they are still skewed and have outliers so they do not meet the normality condition.

66a. JW took the longest time and and TS took the shortest amount of time
``` {r 66a}
FantasyBaseball <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/FantasyBaseball.csv")

stats_bb <- FantasyBaseball %>% 
  group_by(Person) %>% 
  summarise(mean_time=mean(Time, na.rm=T), sd_time=sd(Time, na.rm=T)) %>%
  as.data.frame()
stats_bb

boxplot(FantasyBaseball$Time~FantasyBaseball$Person)
```
66b. The F-stat is 10.89 and the P value is close to 0. This means there is at least one participant with a significant difference from the group.
``` {r 66b}
model <- aov(FantasyBaseball$Time~FantasyBaseball$Person)
summary(model)
```
66c. JW takes significantly longer than everyone else, BK takes significantly shorter than everyone else except BK
``` {r 66c}
library(agricolae)
lsd <- LSD.test(model, "FantasyBaseball$Person")
lsd
```

67a. The data are not normal
``` {r 67a}
bblm = lm(FantasyBaseball$Time~FantasyBaseball$Person)
qqnorm(resid(bblm))
```
67b. The data fits better now
``` {r 67b}
FantasyBaseball$logTime = log(FantasyBaseball$Time)
bbloglm = lm(FantasyBaseball$logTime~FantasyBaseball$Person)
qqnorm(resid(bbloglm))
```
69. The data does not appear to be normal so we must perform a log transformation. Although the data is not yet normal, it fits better once the log transformation is done. Then we run an anova. Since our p value (p=0.284) is greater than our alpha, we don't see any significant difference in selection times based on rounds. 
``` {r 69}
roundlm = lm(Time~Round, data=FantasyBaseball)
qqnorm(resid(roundlm))
plot(resid(roundlm)~fitted(roundlm)) + abline(0,0)

FantasyBaseball$loground = log(FantasyBaseball$Round)

roundloglm = lm(Time~loground, data=FantasyBaseball)
qqnorm(resid(roundloglm))
plot(resid(roundloglm)~fitted(roundloglm)) + abline(0,0)

summary(aov(Time~loground, data=FantasyBaseball))
```


