---
title: "RS3 Day 21"
author: "Saina Shibili"
date: "2023-05-12"
output:
  word_document: default
  html_document: default
---

45. Mixed and Plus are significantly different from Minus
``` {r 45}
library(agricolae)
library(readr)
MouseBrain <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/MouseBrain.csv")

model <- aov(MouseBrain$Contacts~MouseBrain$Genotype)
lsd <- LSD.test(model, "MouseBrain$Genotype")
lsd
plot(lsd)
```
64. Washington is significantly different from all other cities. Houston and boston are not significantly different. Boston and Minneapolis are not significantly different.
``` {r 64}
MetroCommutes <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/MetroCommutes.csv")

MetroCommutes$logtime = log(MetroCommutes$time + 1)

model <- aov(data=MetroCommutes, formula=logtime~city)
summary(model)

lsd <- LSD.test(model, "city")
lsd
plot(lsd)
```
65. Washington and Minneapolis are significantly different from all other cities. Boston and Houston are not significantly different from each other
``` {r 65}
MetroCommutes$sqrttime = sqrt(MetroCommutes$time)

model <- aov(data=MetroCommutes, formula=sqrttime~city)
summary(model)

lsd <- LSD.test(model, "city")
lsd
plot(lsd)
```
70. All three groups are significantly different from each other
``` {r 70}
Hawks <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/Hawks.csv")

model <- aov(data=Hawks, formula=Culmen~Species)
summary(model)

lsd <- LSD.test(model, "Species")
lsd
plot(lsd)
```
72. The data is not normal so conditions for ANOVA testing are not met.
``` {r 72}
AutoPollution <- read_csv("Chapter 5/CSV Data Set Files by Descriptive Title - Chapter 5/AutoPollution.csv")

lmcars = lm(Noise~Type, data=AutoPollution)
qqnorm(resid(lmcars))
```
73a. Size 2 and 1 cars are not significantly different from each other but Size 3 cars are significantly lower. 
``` {r 73a}
stripchart(AutoPollution$Noise~AutoPollution$Size, method = "stack",
           pch = 19,
           xlab="Noise",
           ylab="Type",
           col="maroon")

lmcars = lm(Noise~Size, data=AutoPollution)
qqnorm(resid(lmcars))

model <- aov(data=AutoPollution, formula=Noise~Size)
summary(model)

lsd <- LSD.test(model, "Size")
lsd
plot(lsd)
```
73b. Since 72 was a randomized experiment, we could have determined cause and effect. This could not have been done with 73.