---
title: "day12rs3"
author: "Saina Shibili"
date: "2023-03-25"
output:
  word_document: default
  html_document: default
---

8a. sqrtMD(hat) = -3.1695 + 6.7853(Hospitals)
``` {r question 8a}
library(readr)
CountyHealth <- read_csv("Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/CountyHealth.csv")

CountyHealth$sqrtMD = CountyHealth$MDs**0.5
training = CountyHealth[1:35,]
traininglm = lm(sqrtMD~Hospitals, data=training)
summary(traininglm)
```
8b.
``` {r question 8b}
holdout = CountyHealth[36:53,]
holdout$predict = predict(traininglm, holdout)
holdout$resid = holdout$sqrtMD - holdout$predict
holdout$resid

crossR = cor(holdout$sqrtMD, holdout$predict)
crossR
```
8c.Since the shrinkage is fairly close to zero, we conclude that the model used is suitable for both the training and holdout samples.
``` {r question 8c}
crossRSq = crossR ^ 2
shrinkage = summary(traininglm)$r.squared - crossRSq
shrinkage
```

9a.GPA(hat) = 1.146 + 0.466(HSGPA) + 0.015(HU) + 0.199(White)
``` {r question 9a}
FirstYearGPA <- read_csv("Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/FirstYearGPA.csv")

training = FirstYearGPA[1:150,]
holdout = FirstYearGPA[151:219,]

traininglm = lm(GPA~HSGPA+HU+White, data=training)
summary(traininglm)
```
9b. 
``` {r question 9b}
holdout$predict = predict(traininglm, holdout)
holdout$resid = holdout$GPA - holdout$predict
holdout$resid
```
9c. The mean is fairly close to zero and the standard deviation is about 0.1 away from that of the model, which makes it fairly close.
``` {r question 9c}
mean(holdout$resid)
sd(holdout$resid)
```
9d. 
``` {r question 9d}
crossR = cor(holdout$GPA, holdout$predict)
crossR
```
9e. Since the shrinkage is close to zero it appears the training model explains the holding model fairly well.
``` {r question 9e}
crossRSq = crossR ^ 2
shrinkage = summary(traininglm)$r.squared - crossRSq
shrinkage
```

11a.
``` {r question 11a}
ReligionGDP <- read_csv("Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/ReligionGDP.csv")

ReligionGDP$logGDP = log(ReligionGDP$GDP)
plot(logGDP~Religiosity, data=ReligionGDP)
```
11b. 53.88% of the variability is explained in this model
``` {r question 11b}
religionlm = lm(logGDP~Religiosity, data=ReligionGDP)
summary(religionlm)
```
11c. As religiosity increases by 1, logGDP decreases by 1.4013
11d. Kuwait's studentized residual is about 4
``` {r question 11d}
library(MASS)
stdres = studres(religionlm)
plot(religionlm$fitted.values, stdres)
abline(0,0)
```
11e. 72.35% of the variability is explained in this model
``` {r question 11e}
religionlm2 = lm(logGDP~Religiosity+EastEurope+WestEurope+MiddleEast+Asia+Americas, data=ReligionGDP)
summary(religionlm2)
```
11f. As each variable increases by 1 simultaneously, GDP is predicted to decrease by .9979 because of Religiosity.
11g. Since the p-value is fairly small, we see a significant improvement in the model 
``` {r question 11g}
anova(religionlm, religionlm2)
```
11h. Kuwait's studentized residual is about 3.
``` {r question 11h}
stdres = studres(religionlm2)
plot(religionlm2$fitted.values, stdres)
abline(0,0)
```

12a. Since all the predictors are significant, we will use elevation, difficulty, ascent, and length.
``` {r question 12a}
HighPeaks <- read_csv("Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/HighPeaks.csv")

timelm = lm(Time~Elevation+Difficulty+Ascent+Length, data=HighPeaks)
summary(timelm)
```
12b. We see fairly normal scatter, linearity, and normality in this model
``` {r question 12b}
plot(timelm$residuals~HighPeaks$Time)
abline(0,0)
qqnorm(timelm$residuals)
```
12c. Seward Mt, Mt. Donaldson, and Mt. Emmons all have residuals greater than 2
``` {r question 12c}
stdres = studres(timelm)
stdres
```
12d. Nye Mt. has the largest leverage but is only moderately influential. There don't appear to be any outliers according to Cook's distance.
``` {r question 12d}
hi = hatvalues(timelm)
sort(hi, decreasing=TRUE)
sort(cooks.distance(timelm), decreasing = TRUE)
```