---
title: "Day 1"
author: "Saina Shibili"
date: "2023-02-07"
output:
  word_document: default
  pdf_document: default
---

4a) OUs: Player, Explanatory: Type of Serve, Response: Winning a point (Categorical)
4b) OUs: Home teams, Explanatory: Home/Visitor Game, Response: Which team won (Categorical)
4c) OUs: Golfers, Explanatory: Gender, Response: How far they drive the ball (Quantitative)

5a) Nutrition experts
5b) Controlled experiment bc random assignment to different levels of the IV
5c) How much ice cream scooped (Quantitative)
5d) Bowl Size (Categorical)

8a) Number of Wins (Quantitative)
8b) Points scored/Points allowed (Quantitative)
8c) 1.5
8d) 0.9
8e) Offense
8f) Observational

11a) Yes, the amount scooped increased consistently
11b) Yes, the amount scooped increased consistently
11c) Spoon Size, there is a greater difference in the amount scooped
11d) They are pretty similar

13a) 9.825 wins
13b) The residual is 0.175
13d) 7.96 wins

16a) Age(-) older rollercoasters less fast, Total length(+) more length more room to accelerate and get fast, Maximum height(+) more momentum at the top, Maximum vertical drop(+) more momentum to get fast
16b) Maximum vertical drop because the tallest vertical drop is usually where rollercoasters are the fastest
16c) They were the same except for TypeCode
16d) 59.97

18a) This histogram tells us that the distribution of the percent correct is roughly normal, but with most data points clustered past 50.
``` {r question 18}
library(ggplot2)
library(dplyr)
library(readr)
library(mosaic)

Handwriting <- read_csv("Chapter 0/CSV Data Set Files by Descriptive Title - Chapter 0/Handwriting.csv")

hist(Handwriting$Survey2, 
     col= "maroon", 
     main= "Survey2", 
     xlab= "Survey2", 
     ylab="Frequency")

```
18b) I think the model is better than a 50/50 coin flip. The model is y = u + E, where u > 50.
18c) 65.03

20a)
``` {r Survey2 normal quantile plot}

#normal plot for Survey2
qqnorm(Handwriting$Survey2)

```
20b) 
``` {r Survey2 t-test}

#t-test
t.test(Handwriting$Survey2)

```
20c) Since our p-value is less than 0.05, we reject the null and state that the students do better than 50-50.

22a)
``` {r boxplot of Survey2 vs gender}

boxplot(Survey2~Gender,data=Handwriting,
        col=c("skyblue", "turquoise"),
        main= "Survey2 by gender",
        xlab= "Gender",
        ylab= "Survey2 Scores",
        names= c("male", "female")
        )

```
22b)
``` {r summary stats}

#mean for women
favstats(Handwriting$Survey2[Handwriting$Gender %in% 1])

#mean for men
favstats(Handwriting$Survey2[Handwriting$Gender %in% 0])

```
22c)
``` {r normal quantile of residuals}

#linear regression
handwriting.lm = lm(Survey2 ~ Gender, data=Handwriting)
#residuals
handwriting.stdres = rstandard(handwriting.lm)

#normal probability plot
qqnorm(handwriting.stdres, 
     ylab="Standardized Residuals", 
     xlab="Normal Scores", 
     main="Residual plot of Survey2 by Gender")

#two sample t test
t.test(Survey2~Gender, data=Handwriting)

```
22d) Since our p-value is less than 0.05, our data is significant and we assume that the data is not the same between genders.