---
title: "RS3 Day 11"
author: "Saina Shibili"
date: "2023-03-21"
output:
  word_document: default
  html_document: default
---

2a.The scatterplot comparing Elevation and Time appears largely random and has a very low correlation, with r equaling -0.016.
``` {r question 2a}
library(readr)
HighPeaks <- read_csv("~/Documents/School/Senior Year - 2022-23/rs3/Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/HighPeaks.csv")

plot(Time~Elevation, data=HighPeaks, xlab="Elevation", ylab="Time")
cor(HighPeaks$Time, HighPeaks$Elevation)
```
2b. Since the p-value for elevation and length are relatively small, we assume they are helpful for predicting time in this model. Since the R^2 value increased, we know this model is better at predicting Time than Elevation alone.
``` {r question 2b}
ELlm = lm(Time~Elevation+Length, data=HighPeaks)
summary(ELlm)
```
2c. Since we see a pretty strong correlation in the added-variable plots, we believe that Elevation contributes to the Time predicting plot.
``` {r question 2c}
library(car)
avPlots(ELlm)
```

3a. This model predicts 4 steps of forward selection with ERA, Runs, Saves, and WHIP
``` {r question 3a}
library(MASS)
library("dplyr") 
MLBStandings2016 <- read_csv("~/Documents/School/Senior Year - 2022-23/rs3/Chapter 4/CSV Data Set Files by Descriptive Title - Chapter 4/MLBStandings2016.csv")

full=lm(WinPct~.-Wins-Losses-Team, data=MLBStandings2016)
none=lm(WinPct~1, data=MLBStandings2016)
MSE=(summary(full)$sigma^2)
step(none, scope=list(upper=full), scale=MSE, direction="forward")
```
3b. This model predicts 4 steps of backwards selection with BattingAverage, Runs, Saves, WHIP.
``` {r question 3b}
step(full, scope=list(upper=none), scale=10, direction="backward")
```
3c. This model uses Runs, Doubles, Saves, and Whips.
``` {r question 3c}
library(leaps)
library(HH)
all=regsubsets(WinPct~.-Wins-Losses-Team, nbest=4, data=MLBStandings2016)
summaryHH(all)
```
3d. 11.16,11.88,10.48
3e. Model c because it had the lowest Cp value.

