---
title: "RS3 Day 4"
author: "Saina Shibili"
date: "2023-02-16"
output:
  word_document: default
  html_document: default
---

19a.There does not appear to be a relationship between Calories and Sugar according to the scatterplot created.
``` {r question 19a, echo=FALSE}
#imports needed libraries
library(mosaic)
library(ggplot2)
library(dplyr)
library(readr)

#sets up the cereal database
Cereal <- read_csv("Chapter 1/CSV Data Set Files by Descriptive Title - Chapter 1/Cereal.csv")

#scatterplot between calories and sugar
plot(Calories~Sugar, data=Cereal)
```
19b. Calories(hat) = 2.4808(Sugar) + 87.4277
``` {r question 19b}

#creates the linreg
cereallm = lm(Calories~Sugar, data=Cereal)
#outputs the values from the linreg
summary(cereallm)

```
19c. For every increase in sugar by one gram, the amount of calories in the cereal increases by 2.4808.

21a.112.2357 calories
``` {r question 21a}
#estimation for 10 grams of sugar
2.4808*10 + 87.4277
```
21b. 20.0915
``` {r question 21b}
#residual for Cheerios
110 - (2.4808*1 + 87.4277)
```
21c. No because although it reflects a slight positive association many of the points have large residuals
``` {r question 21c, echo=FALSE}
#graphs the plot between calories and sugar
plot(Calories~Sugar, data=Cereal)
#graphs the linreg on the plot
abline(cereallm)
```
25a. There appears to be a nonlinear negative relationship between distance and adj2007.
``` {r question 25a, echo=FALSE}

#creates the rails trails database
RailsTrails <- read_csv("Chapter 1/CSV Data Set Files by Descriptive Title - Chapter 1/RailsTrails.csv")
#plot of home costs in 2007 and distance from bike trails
plot(adj2007~distance, data=RailsTrails)

```
25b. adj2007(hat) = -54.427(distance) + 388.204; For every increase in distance by 1, the estimated prices of homes in 2007 decreases by 54.427 dollars
``` {r question 25b}
#linear regression of distance
distancelm = lm(adj2007~distance, data=RailsTrails)
#prints out the output of the linreg
summary(distancelm)
```
25c. 92.13, The average deviation from the line of best fit is 92000 dollars.
25d. Since this model does not appear to be linear or have consistent scatter around the line, the conditions for this model are not met.

28a. There appears to be a negative correlation between time and extent
``` {r question 28a}
#creates the seaice database
SeaIce <- read_csv("Chapter 1/CSV Data Set Files by Descriptive Title - Chapter 1/SeaIce.csv")
#plot of extent vs time
plot(Extent~t, data=SeaIce)

```
28b. It further shows curvature
``` {r problem 28b}
seaicelm = lm(Extent~t, data=SeaIce)

plot(fitted(seaicelm), resid(seaicelm), xlab="fitted values", ylab="residuals")
abline(0,0)
```
28c. There is still curvature but it is slightly more linear than before.
``` {r question 28c}
SeaIce$ExtentSq = SeaIce$Extent**2
plot(ExtentSq~t, data=SeaIce)
```
28d. There is still a lot of variation but less so thanbefore
``` {r question 28d}
seaicelm2 = lm(ExtentSq~t, data=SeaIce)

plot(fitted(seaicelm2), resid(seaicelm2), xlab="fitted values", ylab="residuals")
abline(0,0)
```
28e.Curvature still exists but to a lesser extent.
``` {r question 28e}
SeaIce$ExtentCu = SeaIce$Extent**3
plot(ExtentCu~t, data=SeaIce)
seaicelm3 = lm(ExtentCu~t, data=SeaIce)

plot(fitted(seaicelm3), resid(seaicelm3), xlab="fitted values", ylab="residuals")
abline(0,0)
```
28f. No, all three plots show curvature in the scatterplot although the cubed transformations show less curvature in the residual plot.

30a. The pattern appears to be parabolic
``` {r question 30}
Caterpillars <- read_csv("Chapter 1/CSV Data Set Files by Descriptive Title - Chapter 1/Caterpillars.csv")
plot(Nassim~Mass, data=Caterpillars)
```
30b. The pattern appears much more linear, with a positive association and slight curvature
``` {r question 30b}
plot(LogNassim~LogMass, data=Caterpillars)
```
30c. Part b, LogNassim(hat) = -1.88738 + 0.37096(LogMass)
``` {r question 30c}
caterpillarlm = lm(LogNassim~LogMass, data=Caterpillars)
summary(caterpillarlm)
```
30d.It appears to trail off after stages 4 and 5
``` {r question 30d}
ggplot(Caterpillars, aes(x=LogMass, y=LogNassim, color=Instar)) +
  geom_point(shape=19, size=2) +
  coord_fixed() +
  labs(title="LogNassim vs LogMass",
       x="LogMass",
       y="LogNassim") +
  theme_classic()

```
30e. yes
``` {r question 30e}
ggplot(Caterpillars, aes(x=LogMass, y=LogNassim, color=Fgp)) +
  geom_point(shape=19, size=2) +
  coord_fixed() +
  labs(title="LogNassim vs LogMass",
       x="LogMass",
       y="LogNassim") +
  theme_classic()
```

34a. No, the fall semester has an apparently random pattern while the Spring semester has a generally positive pattern
``` {r question 34a}
MathEnrollment <- read_csv("Chapter 1/CSV Data Set Files by Descriptive Title - Chapter 1/MathEnrollment.csv")

plot(Fall~AYear, data=MathEnrollment)
plot(Spring~AYear, data=MathEnrollment)

```
34b. The fall and spring enrollments have a weak negative association
``` {r question 34b}
plot(Spring~Fall, data=MathEnrollment)
```
34c. The data point at the very right
34d. Since the r-squared value is much higher, I would label this point as influential.
``` {r question 34d}
mathlm = lm(Spring~Fall, data=MathEnrollment)
summary(mathlm)

noOutlier = MathEnrollment[-c(3),]
mathlm2 = lm(Spring~Fall, data=noOutlier)
summary(mathlm2)
```

45a.The pattern of time appears to be relatively symmetric
``` {r question 45a}
BaseballTimes2017 <- read_csv("Chapter 1/CSV Data Set Files by Descriptive Title - Chapter 1/BaseballTimes2017.csv")

boxplot(BaseballTimes2017$Time, xlab="Time", horizontal = TRUE)

```
45b. Runs and Pitchers have a weak positive correlation with Time
``` {r question 45b}
plot(Time~Runs, data=BaseballTimes2017)
plot(Time~Margin, data=BaseballTimes2017)
plot(Time~Pitchers, data=BaseballTimes2017)
plot(Time~Attendance, data=BaseballTimes2017)
```
45c.Time(hat) = 148.043 + 4.181(Runs), For every increase in Runs by 1, time increases by 4.181
``` {r question 45c}
timelm = lm(Time~Runs, data=BaseballTimes2017)
summary(timelm)
```
45d. There is no apparent pattern but some of the residuals are quite high
``` {r question 45d}
plot(fitted(timelm), resid(timelm), xlab="Fitted", ylab="Residuals")
abline(0,0)
```

46a. The point at ~20 runs is the CIN-MIL point. It likely makes the line fit the linreg better because it follows that same pattern
46b. The line is almost the same, which makes this point not influential
```{r question 46b}
noCINMIL = BaseballTimes2017[-c(6),]
timelm2 = lm(Time~Runs, data=noCINMIL)
summary(timelm2)

```
46c. Both runs and pitchers look like they have an equal relationship with time to the naked eye now. More statistics would be needed to make a final determination
``` {r question 46c}
plot(Time~Runs, data=noCINMIL)
plot(Time~Margin, data=noCINMIL)
plot(Time~Pitchers, data=noCINMIL)
plot(Time~Attendance, data=noCINMIL)
```
