---
title: "RS3 Day 5"
author: "Saina Shibili"
date: "2023-02-22"
output:
  html_document: default
  word_document: default
---

2. True
3. True
4. False. It's possible that a poor slope prediction has a greater error in the residuals than standard error.

11a. Since the p-value is very small, we reject the null hypothesis that B = 0
``` {r question 11a}
t = 15.5/3.4
pt(t, 38, lower.tail = FALSE)
```
11b. (8.6, 22.4) 
``` {r question 11b}
15.5 + (2.024*3.4)
15.5 - (2.024*3.4)
```

13a. The data appears to be quite random and does not appear to contain any linear relationship
``` {r question 13a}
library(readr)
BrainpH <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/BrainpH.csv")

plot(pH~Age, data = BrainpH)
```
13b. Because the p-value is so large (0.866), there is not sufficient evidence to reject the null hypothesis
``` {r question 13b}
brainPHlm = lm(pH~Age, data = BrainpH)
summary(brainPHlm)
```

15a. Since our t value is 3.507 and our p-value is 0.0013, we have sufficient evidence to reject our null hypothesis (B=0) and conclude there is a linear relationship between calories and sugar in cereal.
``` {r question 15a}
library(readr)
Cereal <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/Cereal.csv")

cereallm = lm(Calories ~ Sugar, data = Cereal)
summary(cereallm)
```
15b. (1.043363, 3.918237); We are 95% confident that the true slope of the relationship between calories and sugar in cereal is in between the range (1.04, 3.918).
``` {r question 15b}
2.4808 + 2.032*0.7074
2.4808 - 2.032*0.7074
```

17a. Yes
``` {r question 17a}
LewyDLBad <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/LewyDLBad.csv")

lewydlbadlm = lm(MMSE~APC, data = LewyDLBad)
summary(lewydlbadlm)
```
17b.
``` {r question 17b}
plot(LewyDLBad$APC, fitted(lewydlbadlm) - LewyDLBad$MMSE)
abline(0,0)
```
17c. Slope = 1.34, SE = 0.4225
17d. (1.734, 3.264)
``` {r question 17c}
t = qt(0.95, 18)
1.34 + t * 0.422
1.34 - t * 0.422
```

19a.price(hat) = 388.204 - 54.427(distance); As the distance increases by 1 mile, the price decreases by 54.427
``` {r question 19a}
RailsTrails <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/RailsTrails.csv")

railstrailslm = lm(adj2007~distance, data=RailsTrails)
summary(railstrailslm)
```
19b. (-38.38344, -70.45996); We are 90% confident that the tru value for the slope lies in the range listed above.
``` {r question 19b}
t = qt(0.95, 102)
-54.4267 + t * 9.659
-54.4267 - t * 9.659
```
19c. We see that the variation in residuals is not equal based on the residual plot
``` {r question 19c}
plot(RailsTrails$distance, fitted(railstrailslm) - RailsTrails$adj2007)
abline(0,0)
```

51a. There appears to be a slight positive relationship between Survey 1 and 2
``` {r question 51a}
Handwriting <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/Handwriting.csv")

plot(Survey2~Survey1, data = Handwriting)
```
51b. Survey2(hat) = 40.417 + 0.39478*Survey1
``` {r question 51b}
Handwritinglm = lm(Survey2~Survey1, data=Handwriting)
summary(Handwritinglm)
```
51c.The residual plot appears to show clustering which makes it not recommendable to fit a linear regression on this model.
``` {r question 51c}
plot(Handwriting$Survey1, fitted(Handwritinglm) - Handwriting$Survey2)
abline(0,0)
```
51d. Since the p-value is very low we can assume there is some relationship, but we might want to inquire into other types of relationships instead of linear.

52a. (0.949382, 0.936818)
``` {r question 52a}
GrinnellHouses <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/GrinnellHouses.csv")

grinnelhouseslm = lm(SalePrice~ListPrice, data=GrinnellHouses)
summary(grinnelhouseslm)

t = qt(0.975, 927)
9.431e-01 + t*3.201e-03
9.431e-01 - t*3.201e-03
```
52b. Since our p-value is less than 0.05, we have sufficient evidence to reject our null hypothesis and assume there is some linear relationship between SalePrice and ListPrice.
52c. (91.878e-07, 8.019 e-08), It's a much smaller range
``` {r question 52c}
GrinnellHouses$fraction = GrinnellHouses$SalePrice/GrinnellHouses$ListPrice

grinnelhouseslm2 = lm(fraction~ListPrice, data=GrinnellHouses)
summary(grinnelhouseslm2)

1.34e-07 + t*2.742e-08
1.34e-07 - t*2.742e-08
```

61a. gate(hat) = 111.826(enroll) + 22576
61b. 49.1%
61c. 184165
61d. 268594, 138594