---
title: "RS3 Day 6"
author: "Saina Shibili"
date: "2023-03-02"
output: word_document
---

9a. Although a high r-squared value indicates a strong correlation, the correlation does not necessarily have to be linear (it could be curved).
9b. A low r-squared value could indicate that another model would be beneficial for the data set, but it could also just be indicating a lower correlation between the variables.

10a. smaller
10b. smaller
10c. larger
10d. larger

23a. 98.53% of the variation in postal rates is explained by the year.
``` {r question 23a, message=FALSE}
library(mosaic)
library(ggplot2)
library(dplyr)
library(readr)

USStamps <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/USStamps.csv")

USStamps <- USStamps[-c(1:4),]

usstampslm = lm(Price~Year, data=USStamps)
summary(usstampslm)
```

23b. Looking at the scatter plot, we see that there appears to be a relatively linear relationship between Price and Year. Furthermore, since our p-value is relatively small, we can conclude that there is a significant linear relationship.
``` {r question 23b, message=FALSE}
plot(Price~Year, data=USStamps)
abline(usstampslm)
```
23c. Since our F value is fairly large and our p-value is fairly small, there is likely a significantly linear relationship between Price and Year.
``` {r question 23c, message=FALSE}
anova(usstampslm)
```

27a. The regression equation is Yardage(hat) = 5.691(attempts) + 86.14
``` {r question 27a, message=FALSE}
BreesPass <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/BreesPass.csv")

plot(Yards~Attempts, data=BreesPass)
breespasslm = lm(Yards~Attempts, data=BreesPass)
abline(breespasslm)

summary(breespasslm)
```
27b. It is not since the mean Yard is 325.5 and the slope coefficient is 5.691
``` {r question 27b, message=FALSE}
mean(BreesPass$Yards)
```
27c. 33.94% of the variability in the data is explained by the attempted passes.

31a. When we test H0(no relationship) and Ha(relationship between Height in 1990 and Height in 1997), we get a fairly small p-value(close to 0), so we conclude there is a significant linear relationship between height in 1990 and height in 1997.
``` {r question 31a, message=FALSE}
Pines <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/Pines.csv")

pineslm = lm(Hgt97~Hgt90, data=Pines)
summary(pineslm)
```
31b. 2.69% of the data is explained by the 1990 heights.
31c. 
``` {r question 31c, message=FALSE}
anova(pineslm)
```
31d. It is the same
``` {r question 31d, message=FALSE}
138344/5148354
```
31e. Looking at the data set, we see that a single line is probably not best to explain this data set because of the high variability.
``` {r question 31e, message=FALSE}
plot(Hgt97~Hgt90, data=Pines)
abline(pineslm)
```

33a. (1.079, 1.113)
``` {r question 33a, message=FALSE}
pineslm2 = lm(Hgt97~Hgt96, Pines)
confint(pineslm2, level=0.95)
```
33b. We can reject the null hypothesis that would say our slope is equal to 1 since 1 is not included in our interval.
33c. No since we are not predicting heights from trees that were not planted.

54a. Runs is most strongly correlated with Time
``` {r question 54a, message=FALSE}
BaseballTimes2017 <- read_csv("Chapter 2/CSV Data Set Files by Descriptive Title - Chapter 2/BaseballTimes2017.csv")
cor(BaseballTimes2017[,c(3:7)])
```
54b. time(hat) = 4.181(runs) + 148.043
``` {r question 54b, message=FALSE}
baseballtimes2017lm = lm(Time~Runs, data=BaseballTimes2017)
summary(baseballtimes2017lm)
```
54c. Since our p-value is less than 0.05, we can assume that this regression equation is considerably significant.
54d. We see that the residuals are not evenly scattered so we assume that conditions for inference are not met.
```{r question 54c, message=FALSE}
plot(BaseballTimes2017$Runs, resid(baseballtimes2017lm))
abline(0,0)

```



