---
title: "RS3 Day 7"
author: "Saina Shibili"
date: "2023-03-07"
output:
  word_document: default
  html_document: default
---

1a. 100, they would get a perfect score on the final
``` {r question 1a}
11.0 + 0.53*100 + 1.2*30
```
1b. -2.31, Michael got a grade that was 2.31 points less than predicted by the model
``` {r question 1b}
11.0 + 0.53*87 + 1.2*21
80-82.31
```

3. We do not know enough information to answer this question because in order to determine the degree of correlation we need to know the standard errors of the slopes.

5. If the Midterm score remains constant, as the project score increases by one point, the grade of the final score increases by 1.2 points.

7a. This is true because the adjusted r-squared is divided by (n-k-1)/(n-1) and the regular r-squared does not account for this value.
7b. This is false because there could be predictors that do not explain the data set very well.

17a. Since our p-value is .282, which is fairly large, we do not have enough evidence to assume a linear relationship between Weight and Active Pulse
17b. (-0.0182, 0.0866). We are 90% confident that the true slope that portrays the relationship between weight and active pulse is in the interval (-0.0182, 0.0866)
``` {r question 17b}
t = qt(.95, 228)

0.0342 + t*0.03173
0.0342 - t*0.03173
```
17c. 96.13
``` {r question 17c}
11.8 + 1.12*76 + 0.0342*200 - 1.09*7
```

18a & 18b. Yes, the coefficient changes from -54.427 to -16.486 and the r squared value increases
``` {r question 18a & 18b}
#r question 18a
library(readr)
RailsTrails <- read_csv("Chapter 3/CSV Data Set Files by Descriptive Title - Chapter 3/RailsTrails.csv")

railstrailslm = lm(adj2007~distance, data=RailsTrails)
summary(railstrailslm)

#r question 18b
railstrailslm2 = lm(adj2007~distance + squarefeet, data=RailsTrails)
summary(railstrailslm2)
```
18c. The confidence intervals for distance is smaller in width and in the negatives while the confidence intervals for squarefeet are larger in width and larger in actual number.
``` {r question 18c}
confint(railstrailslm2, level = 0.95)
```
18d. $226,271.50 
``` {r question 18d}
109.742 - 16.486*0.5 + 150.780*1500
```
