---
title: "RS3 Day 8"
author: "Saina Shibili"
date: "2023-03-11"
output:
  word_document: default
  html_document: default
---

10a. Negatively, Newer cars should have lower mileages
10b. Negatively, cars with higher mileages are usually cheaper

11a. Negative because they are cheaper than the expected price.
11b. Price(hat) = B0 + B1(Mileage) + B2(Year)
11c. To account for interaction between Year and Mileage. The coefficient will likely be negative since they have a negative correlation

13a. Arsenic(hat) = B0 + B1(Year) + B2(Distance) + B3(YearxDistance)
13b. Lead(hat) = B0 + B1(Year) + B2(IClean) + B3(YearxIClean)
13c. Titanium(hat) = B0 + B1(Miles) + B2(Miles^2)
13d. Sulfide(hat) = 0 + B1(Year) + B2(Miles) + B3(Depth) B4(YearxMiles) + B5(YearxDepth) + B6(DepthxMiles)

15. formula: n - k - 1: 194, 194, 195, 191

34a. PctDM(hat) = -0.210(Age) + 38.702
``` {r question 34a}
library(readr)
FishEggs <- read_csv("Chapter 3/CSV Data Set Files by Descriptive Title - Chapter 3/FishEggs.csv")

fisheggslm = lm(PctDM~Age, data=FishEggs)
summary(fisheggslm)
```
34b. 20.04%. of the variability is accounted for
34c. Since p-value is less than 0.05, we have significant data
34d. 
``` {r question 34d}
plot(FishEggs$Age, resid(fisheggslm))
abline(0,0)
```
34e. The residuals for November are concentrated above 0 and Sep below 0.
``` {r question 34e}
library(ggplot2)
ggplot(FishEggs,aes(x=Age,y=resid(fisheggslm))) +
  geom_point(aes(color=Month)) + 
  scale_color_manual(name=NULL,
                     values=c("pink", "hotpink"),
                     breaks=c("Nov", "Sep"),
                     labels=c("Nov", "Sep")) + 
  labs(x="Age",
       y="Resid") +
  geom_hline(yintercept=0)

FishEggs$AgeSept = FishEggs$Age * FishEggs$Sept
fisheggslm2 = lm(PctDM~Age+Sept+AgeSept, data=FishEggs)
summary(fisheggslm2)
```
34f. They are not significant but if you remove the interaction term it becomes significant.
``` {r question 34f}
fisheggslm2 = lm(PctDM~Age+Sept, data=FishEggs)
summary(fisheggslm2)
```
34g. 42.98% of the variability is accounted for
34h. The resids are more evenly spread out
``` {r question 34h}
ggplot(FishEggs,aes(x=Age,y=resid(fisheggslm2))) +
  geom_point(aes(color=Month)) + 
  scale_color_manual(name=NULL,
                     values=c("pink", "hotpink"),
                     breaks=c("Nov", "Sep"),
                     labels=c("Nov", "Sep")) + 
  labs(x="Age",
       y="Resid") +
  geom_hline(yintercept=0)
```

41a. ProteinProp = 0.47993 - 0.25319(Calcium) - 0.02779(CalciumSq)
``` {r question 41a}
Fluorescence <- read_csv("Chapter 3/CSV Data Set Files by Descriptive Title - Chapter 3/Fluorescence.csv")

Fluorescence$CalciumSq = Fluorescence$Calcium^2
fluorescencelm = lm(ProteinProp~Calcium+CalciumSq, data=Fluorescence)
summary(fluorescencelm)
```
41b.
``` {r question 41b}
plot(ProteinProp~Calcium, data=Fluorescence)+
  lines(fitted(fluorescencelm)~Fluorescence$Calcium,col="hotpink")
```
41c. Conditions are met since the normal plot looks fairly linear
``` {r question 41c}
qqnorm(resid(fluorescencelm))
```
41d. Since the p-value is close to 0, it is signfinicant.
41e. 89.4% of the variation is explained

42a. ProteinProp = -6.523761 - 3.13844(Calcium) - 0.41133(CalciumSq) - -0.016515(CalciumCu)
``` {r question 42a}
Fluorescence$CalciumCu = Fluorescence$Calcium^3
fluorescencelm2 = lm(ProteinProp~Calcium+CalciumSq+CalciumCu, data=Fluorescence)
summary(fluorescencelm2)
```
42b.
``` {r question 42b}
plot(ProteinProp~Calcium, data=Fluorescence)+
  lines(fitted(fluorescencelm2)~Fluorescence$Calcium,col="hotpink")
```
42c. Conditions are not met since there is curvature in the plot
``` {r question 42c}
qqnorm(resid(fluorescencelm2))
```
42d. Since the p-value is close to 0, it is signfinicant.
42e. 94.5% of the variation is explained

43a. margin(hat) = 4.477 - 0.604(day) + 0.021(day2). R^2= 34.95%, SSE = 899
``` {r question 43a}
Pollster08 <- read_csv("Chapter 3/CSV Data Set Files by Descriptive Title - Chapter 3/Pollster08.csv")

Pollster08$DaySq = Pollster08$Days^2
pollster08lm = lm(Margin~Days+DaySq, data=Pollster08)
summary(pollster08lm)
```
43b. R^2 = 41.7%, SSE=806.1
``` {r question 43b}
Pollster08$DayCharlie = Pollster08$Days*Pollster08$Charlie
pollster08lm2 = lm(Margin~Days+Charlie+DayCharlie, data=Pollster08)
summary(pollster08lm2)
```
43c. R^2 = 32.39, SSE=934.5
``` {r question 43c}
Pollster08$DayMeltdown = Pollster08$Days*Pollster08$Meltdown
pollster08lm2 = lm(Margin~Days+Meltdown+DayMeltdown, data=Pollster08)
summary(pollster08lm2)
```
43d. B because it has the highest r^2 and the lowest SSE

44a. Beds
``` {r question 44a}
CountyHealth <- read_csv("Chapter 3/CSV Data Set Files by Descriptive Title - Chapter 3/CountyHealth.csv")

CountyHealth$MDSq = CountyHealth$MDs^1/2
cor(CountyHealth[,c(3:5)])
```
44b. 82.31%, 92.41%
``` {r question 44b}
hosplm = lm(MDSq~Hospitals, data=CountyHealth)
bedlm = lm(MDSq~Beds, data=CountyHealth)
summary(hosplm)
summary(bedlm)
```
44c. 94.15%
``` {r question 44c}
CountyHealth$HospBed = CountyHealth$Hospitals*CountyHealth$Beds
hospbedlm = lm(MDSq~Hospitals+Beds+HospBed, data=CountyHealth)
summary(hospbedlm)
```
44d. Both
44e. Since both have small p-values, they are both important in predicting MdsSq.