---
title: "RS3 Day 9"
author: "Saina Shibili"
date: "2023-03-14"
output:
  word_document: default
  html_document: default
---

12a. Mrate(hat) = B0 + B1(BodySize) + B2(Ifgp) + B3(BodySize*Ifgp)
12b. Mrate(hat) = B0 + B1(BodySize) + B2(Ifgp)
12c. The full model is the same as part a; the reduced model is
     Mrate(hat) = B0
     
14. Part A: 53 - 3 - 1 = 49; Part B: 53 - 2 - 1 = 50

48a. Although the boxplots overlap, the p-value of our t-test is fairly small so our data is statistically significant.
``` {r question 48a}
library(readr)
RailsTrails <- read_csv("Chapter 3/CSV Data Set Files by Descriptive Title - Chapter 3/RailsTrails.csv")

boxplot(adj2007~garagegroup,data=RailsTrails, main="Price of Home vs. Garage", xlab="Garage Owned?", ylab="Cost of House")
t.test(adj2007~garagegroup, data=RailsTrails)
```
48b. There is a significant negative relationship between distance and home price in 2007.
``` {r question 48b}
distancelm = lm(adj2007~distance, data=RailsTrails)
summary(distancelm)
```
48c. House price has a significant relationship with both distance and garagegroup. The slope of distance is -51.025 while the slope of garagegroup is 37.892. The R^2 value increased.
``` {r question 48c}
distance_garagegroup_lm = lm(adj2007~distance+garagegroup, data=RailsTrails)
summary(distance_garagegroup_lm)
```
48d.-46.302 or -56.18, Since the p-value is quite large, its not statistically significant.
``` {r question 48d}
RailsTrails$DistanceGarage = RailsTrails$distance*(RailsTrails$garagegroup == "yes")
distance_garagegroup_lm2 = lm(adj2007~distance+garagegroup+DistanceGarage, data=RailsTrails)
summary(distance_garagegroup_lm2)
```
48e. Since the p-value is fairly large, there is no significance among the data regarding the garagegroup.
``` {r question 48e}
anova(distancelm, distance_garagegroup_lm2)
```

49a. logdistance and logsquarefeet are significant predictors of logadj2007 at the 0 level and no_full_baths is a significant predictor of logadj2007 at the 0.01 level. 78.34% of the variability is accounted for by this model. Price goes down with distance and up with both squarefeet and number of bathrooms. 
``` {r question 49a}
RailsTrails$logadj2007 = log(RailsTrails$adj2007)
RailsTrails$logdistance = log(RailsTrails$distance)
RailsTrails$logsquarefeet = log(RailsTrails$squarefeet)

railstrailslm = lm(logadj2007~logdistance+logsquarefeet+no_full_baths, data=RailsTrails)
summary(railstrailslm)
```
49b. Both plots show conditions are met
``` {r question 49b}
plot(fitted(railstrailslm), resid(railstrailslm), main="Residual plot")
abline(0,0)
qqnorm(resid(railstrailslm))
```
49c. Price goes down as logdistance,ds,db, and no_full_baths go up. Price increases as all the other predictors increase. The R^2 value is no 80.07%, which is only a slight increase from previously.
``` {r question 49c}
RailsTrails$ds= RailsTrails$logdistance*RailsTrails$logsquarefeet
RailsTrails$sb = RailsTrails$logsquarefeet*RailsTrails$no_full_baths
RailsTrails$db = RailsTrails$logdistance*RailsTrails$no_full_baths
RailsTrails$bds = RailsTrails$logdistance*RailsTrails$no_full_baths*RailsTrails$logsquarefeet

railstrailslm2 = lm(logadj2007~logdistance+logsquarefeet+no_full_baths+ds+sb+db+bds, data=RailsTrails)
summary(railstrailslm2)
```
49d. Since our p-value is fairly large, the addition in complexity likely does not add much to our linear model
``` {r question 49d}
anova(railstrailslm, railstrailslm2)
```

52a. If type = DLB/AD --> MMSE(hat) = -0.4946 + 2.3176(APC), else MMSE(hat) = -1.42 + 2.3176(APC)
``` {r question 52a}
LewyBody2Groups <- read_csv("Chapter 3/CSV Data Set Files by Descriptive Title - Chapter 3/LewyBody2Groups.csv")
LewyBody2Groups$AType = LewyBody2Groups$APC * (LewyBody2Groups$Type == "DLB/AD")

lblm = lm(MMSE~APC+Type+AType, data=LewyBody2Groups)
summary(lblm)
```
52b. The p-value for the interaction is fairly large and deems it not needed.
52c. Since the p-value is so large, it is evident that the interaction term is unnecessary.
``` {r question 52c}
lblm2 = lm(MMSE~APC+Type, data=LewyBody2Groups)
anova(lblm, lblm2)
```

56. The adjusted r-squared decreases in this model
``` {r question 56}
MLBStandings2016 <- read_csv("Chapter 3/CSV Data Set Files by Descriptive Title - Chapter 3/MLBStandings2016.csv")

mlblm = lm(WinPct~Runs+ERA, data=MLBStandings2016)
summary(mlblm)

mlblm2 = lm(WinPct~RBI+ERA+Runs+HitsAllowed+WHIP, data=MLBStandings2016)
summary(mlblm2)
```
